PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2022-01-25 main.tex
Add text discussing figure 12, include alpha curves for various compositions

@@

@@

% compare f=4 and f=6 disk. show that the mass transition moves inwards by the correct amount as alpha changes

@@

>>>>

% Period vs mass for each model?
% Positive trend for trappist-1 planets, excluding a,b

@@

In all cases shown so far, the boundary between the standard oligarchic growth and the highly-efficient short period accretion region lies around 60 days in orbital period. The mode of accretion is set entirely by the local value of $\alpha$, which scales with both distance from the star and the bulk density of the planetesimals (see equation \ref{eq:alpha}). The artificial inflation of the collision cross section of the particles in our simulations, which is meant to reduce the computational expense, has the side effect of reducing the bulk densities. Because $\alpha \sim \rho_{pl}^{-1/3}$, increasing the particle sizes by a factor of f=6 reduces the orbital period at which $\alpha$ has a given value by a factor of approximately 15. Therefore, one would expect the accretion boundary to lie near 5 days in orbital period for 3 g $cm^{-3}$ bodies.

Although a simulation with f=1 is not computationally tractable, we can test whether the accretion boundary moves in the way we expect by modestly changing the value of $f$. In figure \ref{fig:f6f4}, we compare the fdHi simulation to a nearly identical run using f=4. In the top panel, the embryo masses in units of the isolation mass are shown as a function of orbital period. In the bottom panel, the value of $\alpha$ as a function of orbital period is shown for 3 g $cm^{-3}$ bodies with an artificial radius enhancement of f=1, 4 and 6. The horizontal dashed line indicates the value of alpha below which the accretion mode switches to oligarchic growth. Comparing the top and bottom panels, the intersection of the embryo masses and local isolation mass matches well with the orbital period at which $\alpha \sim 0.1$. Also shown by the curved dotted lines are the $\alpha$ curves for realistic-sized bodies with $\rho_{pl}$ = 1, 5 and 10 g $cm^{-3}$. In all cases, the accretion boundary still lies within the part of the disk in which solids would be expected to accumulate (citation?).

@@

% compare f=4 and f=6 disk. show that the mass transition moves inwards by the correct amount as alpha changes
% how does density affect results? trappist-1 planets are 5 g/cc (agol+ 2021)

@@

% Compare with ICs used in Ogihara 22
